Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-13 main.Rmd
all todo questions answered

\todo[inline]{What is g-rel?}

@@

\todo[inline]{What does "full-integer" mean?}

@@

\todo[inline]{What does this last phrase mean?}

@@

\todo[inline]{Why is this called a ``pseudomonth''?}

>>>>

\todo[inline]{What is g-rel? - g-rel can be any granularity relationships like -   
groups into, finer than, groups periodically (the granularity relationships defined in this paper) or sub-granular, shift equivalent (not discussed in this paper but other relationships that the author discussed in @Bettini1998-ed)}

@@

\todo[inline]{What does "full-integer" mean? It might be the case that we don not always
have integers as the label sets of granularities. A full-integer labeled granularities are defined in definition 2 since labels coincide with indices. These labels can be an
arbitrary subset of (possibly noncontiguous) integers and could be used to identify granules. The author has introduced the definition of "labeled granularity" in @Ning2002-tf which could be added after definition of linear granularity to clarify this. }

@@

\todo[inline]{What does this last phrase mean? - if  the time horizon is such that it starts from the 15th second of a day, then doing repeated operations of grouping might result in a granule of "resultant" granularity day or week, which is different from a time-stamped day or week. Could be phrased better or deleted.}

When the granules for second and minutes are arranged, the first granule of seconds and minutes granules should that overlap share elements from the underlying time domain}

@@

\todo[inline]{Why is this called a ``pseudomonth''? - Here,  granularity pseudomonth is generated by grouping 31 days, and then shrink April, June, September and
November by 1 day, and shrink February (2) by 3 days. It doesn't incorporate adjustments for leap year or seconds in which case the period for the altering operation should be 400 instead of 12. ``pseudomonth`` computes months only in non-leap years.}
